From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks

### 2018-04-23 article/article.tex
article/article.tex
New figure for explaining method

\listfiles
\documentclass[manuscript, proceedings]{acmart}
\usepackage[utf8]{inputenc}
\usepackage{color}

@@

>>>>

\documentclass[manuscript, proceedings]{acmart}
\usepackage[utf8]{inputenc}
\usepackage{color}

@@

\begin{figure*}[ht]
\includegraphics[width=\textwidth]{images/ppi_example_combined.eps}
\caption{An example of the query term \textit{``SNAP receptor activity''} on the arabidopsis protein-protein interaction network.
(A) Shows the full network with 3 randomly chosen query nodes from the full query set.
(B) Shows a reduced view of the network where a threshold is selected.
(C) Shows an example ROC curve, sampled from combinations of using 3 randomly selected query nodes including this term.
Blue nodes indicate those in the query set, the shade of red relates to the strength of the relationship each node has to the query set.
}
\label{fig:query_example}
\end{figure*}
